%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activity \& Volunteering}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

    %---------------------------------------------------------
  \cventry
  {Makerspace Manager} % Job Title
  {ETH Zurich Student Project House} % Organisation
  {Zurich, Switzerland} % Location
  {April. 2022 --- Present} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item I volunteere as a makerspace manager at the Student Project House at ETH Zurch.
      \item My responsibilities include giving introductory lectures/workshop on the in-house machinery and equipment, giving general introductions to the makerspace, supervising the makerspace and manning the counter during open-hours.
    \end{cvitems}
  }
  
  %---------------------------------------------------------
  \cventry
  {Member} % Job Title
  {KCL Informatics and Engineering Teaching Assistant Liaison Committee} % Organisation
  {London, UK} % Location
  {Jan. --- Aug. 2020} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item I acted as a contact point to the TA community in case of concerns with module leaders and TA-related procedures.
    \end{cvitems}
  }

  \cventry
  {Temporary Member/Active Participant} % Job Title
  {KCL Informatics and Engineering Student-Staff Liaison Committee} % Organisation
  {} % Location
  {Dec. 2019} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {I volunteered time to raise and discuss possible solutions to student concerns about the KCL `Artificial Intelligence Planning' module with both the administration of the faculty and the module leaders Dr Stefan Edelkamp \& Dr Daniele Magazzeni as a member of the student body.}
    \end{cvitems}
  }

%  ---------------------------------------------------------
  \cventry
  {German and Russian Language Tutor} % Job Title
  {Modern Language Center at King’s College London} % Organisation
  {} % Location
  {Apr. --- Aug. 2019} % Date(s)
  {
     \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {I volunteered time to run speaking practice sessions with students at the university and persons of the public.}
    \item {I evaluated and gave feedback on the students' use of the language and lexicon ultimately to help them express themselves in the language.}
    \item {I helped students build confidence in speaking the language in a safe environment.}
    \end{cvitems}
 }

%  ---------------------------------------------------------
  \cventry
  {Workshop Leader and Organizer} % Job Title
  {Beginner's Programming and Game Development Workshop} % Organisation
  {Berlin, Germany} % Location
  {May. --- Jul. 2017} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item I founded and launched an after-school beginner’s programming workshop after learning that the school did not offer adequate education in the topic `due to low demand.'
      \item I thought the basics of programming to a class of c. 30 students of mixed ages using Python 3 and the 2D game engine Game Maker Studio.
      \item This effort was acknowledged by the school and the administration, and was noted in that year's yearbook.
    \end{cvitems}
  }

  %---------------------------------------------------------
%   \cventry
%   {Participant} % Job Title
%   {ISMTF Senior Mathematics Competitions \& International Junior Kangaroo Competitions} % Organisation
%   {Vienna, Austria \& Moscow, Russia} % Location
%   {Mar. 2015, Mar. 2014, 2009, 2008} % Date(s)
%   {
%     \begin{cvitems} % Description(s) of tasks/responsibilities
%       \bsep{} Participated in the competition in a team of international students to further my insight into mathematics.
%       \bsep{} Used the experience to further my communication skills and to   learn from representatives of foreign to me curricula and teaching methods.
%     \end{cvitems}
%   }
\end{cventries}
